Technical Report

### 2017-09-27 fully-abstract-comp/technical-report.tex

\subsection{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\dominique{Regarding the type signature for $[\cdot]$ above: does this mean that it maps lists of instructions to lists of instructions? Is there another function that compiles a single instruction to a list of instructions?}

>>>>

\subsection{Programs and contexts}
\begin{definition}
  \label{def:self-contained}
  \begin{itemize}
  \item We say that a memory segment $\ms$ and a list of capabilities $\bar{c}$
    are self-contained iff
  \[
    \forall c \in \bar{c} \ldotp \range{c} \subseteq \dom{\ms}
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom{\ms}
  \end{multline*}
  \item We say that a memory segment $\ms$ and a list of capabilities $\bar{c}$ are self contained with slack $\ms_s$ iff
  \[
    \forall c \in \bar{c} \ldotp \range{c} \subseteq \dom{\ms \cup \ms_s}
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom{\ms \cup \ms_s}
  \end{multline*}
\end{itemize}
\end{definition}

\subsubsection{Programs}
Here we define what consitutes a program.

\begin{definition}
  \label{def:program}
  \lau{27-09-2017: The ``somehow''s need to be fixed.}
  A program consists of two sealed capabilities, $\vsc_\code = \sealed{c_\code,\sigma}$ and $\vsc_\data = \sealed{c_\data,\sigma}$, and and two memory segments $\ms$ and $\ms_\link$ satisfying
  \begin{itemize}
  \item $c_\code = ((\rx,\lin_\code),\baddr_\code,\eaddr_\code,\aaddr_\code)$ where $\aaddr = \baddr + 3$ and $[\baddr_\code,\eaddr_\code]\subseteq \dom(\ms)$
  \item $c_\data = ((\rw,\lin_\data),\baddr_\data,\eaddr_\data,\baddr_\data)$ where $[\baddr_\data,\eaddr_\data] \subseteq \dom(\ms)$ and $[\baddr_\code,\eaddr_\code] \cap [\baddr_\data,\eaddr_\data] = \emptyset$
  \item $\ms$ and $[c_\code,c_\data]$ are self-contained with $\ms_\link$ as slack.
  \item $\ms(\baddr_\code) = \seal(\normal,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr)$ where these are somehow the sufficient amount of seals.
  \item $\ms(\baddr_\code+1) = ((\ro,\normal),\baddr_\link, \eaddr_\link, \baddr_\link)$ where $\dom(\ms_\link) = [\baddr_\link, \eaddr_\link]$
  \item $\ms(\baddr_\code+2) = \dots$ where $\dots$ is somehow the stack height.
  \end{itemize}
\end{definition}
\lau{27-09-2017: At the moment, we do not have the proper support to let the code capability be linear (in the sense that you cannot write a sensible program) - maybe we should just require the code capability to be normal.}

\subsubsection{Contexts}

\section{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\dominique{Regarding the type signature for $[\cdot]$ above: does this mean that it maps lists of instructions to lists of instructions? Is there another function that compiles a single instruction to a list of instructions?}
